---
title: "ggplot + plotly"
author: "Emi Tanaka"
date: "19/09/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=F, warning=F}
library(ggplot2)
library(plotly)
```

## First ggplot 

Here is my first `ggplot`!

```{r}
g <- ggplot(iris) +
  aes(Sepal.Length, Sepal.Width) +
  geom_point() +
  labs(x = "Sepal Length") +
  labs(y = "Sepal Width") +
  labs(title="The famous iris data") + 
  labs(subtitle="Data collected by Anderson, Edgar (1935)") +
  aes(color= Species) +
  theme_bw(base_size=16)
g
```

## First plotly 

Here is my first `plotly`! This is an interactive plot so try hovering it over and clicking. You may want to write `message=F, warning=F` as your R chunk option here to avoid some unwanted outputs. 

```{r, message=F, warning=F}
plot_ly(iris, 
        x=~Sepal.Length, 
        y=~Sepal.Width, 
        color=~Species)
```

## First ggplotly

Here is my first `ggplotly`! This is also an interactive plot. Remember that you cannot achieve this interactivity for pdf and doc. This is only designed for html output.

```{r}
ggplotly(g)
```